---
title: "PMLProject"
author: "TFH"
date: "15 4 2020"
output:
  html_document:
    df_print: paged
---

Read Data and cleaning

```{r dataRead}
library(caret)
train <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv")
fintest <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv")
names <- names(fintest[, colSums(is.na(fintest)) == 0])
train <- train[, c(names[-length(names)], "classe")] 
train <- train[, -1:-7]
```

Split the trainingset for cross validation
```{r}
inTrain <- createDataPartition(train$classe, p = 0.7, list = F)
train_1 <- train[inTrain, ]
test <- train[-inTrain, ]
```

Know we have three dataframes, train_1, cross_vali and test.

After I testes some models, I decides, that the randomForest makes the best out of it. Use the caret library. But it was so long, that I did a classification for the final pdf.

```{r}
set.seed(1)
model <- train(classe ~., data = train_1, method="rpart")
```

Check the Accurancy

```{r}
table(predict(model, test), test$classe)

```

#Conclusion

Train the RF model is really slow, maybe their are some faster, but else it's okey.
Clasification tree is fast, but teh accurancy is not good.